\section{CrashSimulator Approach Details}

    %%% Verify information on supported trace formats %%%
    \subsection{System Call Traces}

        The first step in CrashSimulator's operation is to gather a trace of the system calls made by the application
        during a normal run. Where other tools base their operation of direct analysis of the application under test
        CrashSimulator operates based on information gleaned from system call traces. This gives CrashSimulator several
        advantages over similar tools. First, CrashSimulator operates in a language independent manner. It can test any
        program given two conditions hold true:

        \begin{enumerate}
            \item{The application can run in the testing environment}
            \item{The testing environment has the tooling required to take a system call trace of the application during
            a normal run}
        \end{enumerate}

        This removes the need for the complex language parsing that other similar tools rely on. Second, the faults
        injected by CrashSimulator test the interface between the application under test and its environment. Other
        similar testing tools focus on testing the logic within the application under test which missing faults that
        only appear when the application is run in an imperfect, real world environment.

        Because CrashSimulator's trace analysis engine is based on prior work from the NetCheck supported trace
        gathering tools include \emph{strace} on Linux and \emph{dtrace} on OS X.


    \subsection{Supported Anomaly Types}

        \textbf{I would really like to find another term besides anomaly}

        CrashSimulator's goal when analyzing a normal run system call trace is to identify individual system calls or
        patterns of system calls that it recognizes as an opportunity to inject a fault during subsequent runs. These
        signatures are referred to as ``potential anomalies.'' CrashSimulator has the ability to identify and make use
        of several classifications of potential anomalies.

        \subsubsection{Return Value Modification}

        \subsubsection{Data Reordering}

        \subsubsection{Data Truncation}

    \subsection{Trace Analysis}



    \subsection{Fault Injection}

         Once a set of potential fault injection points has been identified CrashSimulator uses \emph{ptrace} inject
         faults on a live execution of the program. At this point, two faults types identifiable by NetCheck are
         supported: modification of return values from network system calls and reordering of UDP packets.  These faults
         were chosen because of high impact they can have on applications that don't handle them properly and the
         frequency with which developers have an incorrect understanding of how these system calls can behave in an
         imperfect environment.

        %% I can go into much more detail with the ptrace implementation stuff if I need to
        \subsection{Return Value Modification}

        One way CrashSimulator can inject faults into the running application is to
        modify the return values of interesting system calls identified in the previous trace analysis step. First, the
        CrashSimulator parent application is launched and configured.

        \begin{verbatim}
        launching of parent application
            setup of child application under test
            run child application
            For for each system call determine if it is one we are interested in as determined by analysis
                e.g.\ is this the 4th call to recv?
            Modify EAX/RAX register after system call completion to contain new return value
                New return value random? Smaller than present return value? Some constant -1?
                What do we do about 32-bit vs 64-bit
        \end{verbatim}

        %% What is the process for culling our set of unit tests for instances where there are a huge number of
        %% permutations of packet orderings
        \subsection{Catalog-Based Anomalies}

        A second category of faults CrashSimulator can produce are known as catalog-based faults. These faults are
        injected in two steps. First, the normal run trace is parsed in its entirety for system calls in a specific set
        associated with the fault being injected and the data items passed into these system calls are recorded in a
        data item catalog. Next, the application under test is run repeatedly with each run receiving a different
        ordering of data items from the catalog for the corresponding system calls. One example of a fault
        CrashSimulator can inject in such situations is unhandled out of order UDP datagrams. Consider the following
        pseudo-code listing:

        %% Use the real C Code here
        \begin{verbatim}
int main() {
    socket = setupUdpSocket()
    data1 = recvfrom(socket)
    processData1(data1)
    data2 = recvfrom(socket)
    processData2(data2)
}
        \end{verbatim}

        This listing sets up a UDP socket and receives two datagrams from the socket processing each with the
        appropriate function. A C program that implements this pseudo-code will produce a normal flow system call trace
        as follows:

        \begin{verbatim}
...
socket(PF_INET, SOCK_DGRAM, IPPROTO_UDP) = 3
bind(3, {sa_family=AF_INET, sin_port=htons(6666), sin_addr=inet_addr("0.0.0.0")}, 16) = 0
recvfrom(3, "test\n", 256, 0, {sa_family=AF_INET, sin_port=htons(51490), sin_addr=inet_addr("127.0.0.1")}, [16]) = 5
...
write(1, "Process 1: test\n", 16)       = 16
recvfrom(3, "testagain\n", 256, 0, {sa_family=AF_INET, sin_port=htons(51490), sin_addr=inet_addr("127.0.0.1")}, [16]) = 10
write(1, "Process 2: testagain\n", 21)  = 21
...
        \end{verbatim}

        The above program assumes that datagram 1 will always arrive first and datagram 2 will always arrive second. UDP
        makes no ordering guarantees so the reverse is possible. This would result in datagram 2 being processed as
        datagram 1 and vice versa. Crash simulator would inject this fault as follows. First, it would parse the system
        call trace and identify all calls to recvfrom, storing the data that was received in a data catalog and the
        identifying information pertaining to the socket it was received from. Second, it would re-run the application
        under test and send a different ordering of data from the data catalog to the socket in question. From the above
        example, ``testagain'' would be sent to the first receive from and ``test'' would be sent to the second recvfrom
        resulting in each data item being parsed by the incorrect function. CrashSimulator would then report
        abnormalities in the application's behavior. \textbf{How are we going to handle situations where this is a
        silent failure}

    \subsection{Limitations}

        %% This text will need to be updated based on discussion about handling testing of interpreted languages
        CrashSimulator operates at the level of an applications interactions with the operating system and environment
        on which it is run. It does not make any attempt to determine what the cause of a fault may have been at a
        higher level. For example, in situations where CrashSimulator is testing an application written in an
        interpreted language the possibility exists that faults will be found in the interpreter rather than the
        application itself. For example, CrashSimulator may modify system calls made by the interpreter for purposes
        that are independent from the application under test. If this results results in improper output CrashSimulator
        will simply report it as a fault in the application despite the fact that the user's code was not responsible
        for the error.
